Coherent optical association of a single molecule

### 2020-10-19 paper.tex
White space, remove duplicated reference entry, regenerate PDF
Update on Overleaf.

Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules. The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}. These requirements greatly limit the generality of previous association techniques.
%The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

@@

\textcolor{blue}{(need to make consistent concise terminology, excited state molecule, weakly bound molecule, molecular state, etc.  call them  state 1, 2, 3? or revert back to call the intermediate state without mentioning molecule?).} The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%, 
%$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}. 
Unlike for Raman transitions in atoms, the two coupling matrix elements here are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. 
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
\footnote{The sum of the squares of the wavefunction overlap between the weakly bound molecular state and all the excited intermediate states considered is only about 2\%, suggesting that there is significant matrix element between this weakly bound state and the excited atomic continuum. See supplementary information.} \textcolor{red}{(KW: I included a footnote here, but we can also consider putting this information into the main text?)}

@@

%and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.} 
%As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. 
%Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$. \textcolor{blue}{(the two sentences have the same idea.)}
%it can be made larger by increasing the coupling of the atomic state with the excited molecular state. 
Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs. Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/8} $, where $ \omega_{\text{trap}} $ is the trap frequency. Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).

@@

For our system of Na and Cs atoms, we chose  a  spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}. We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$) \textcolor{blue}{(define arbitrarily).} 
%We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$. Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. 

@@

%Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination. 

@@

%After preparing the Na and Cs atoms in the same tweezer in a single quantum state, 
Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. 
This spin flip selectively transfers atoms in the relative motion ground state \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
%After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. 
To perform Raman transfer of an atom pair to the targeted weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to  maximize the Raman Rabi frequency and minimize the transfer time. %to allow perfect overlap and to eliminate additional beams and therefore scattering sources. 
The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. 
%In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. 
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
%In addition to reducing the number of laser beams during the Raman transition, 
Furthermore, we use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by at least  a factor of $2$ \textcolor{blue}{(can we be more definite?)}
(for a particular single photon detuning) due to the (xx dB?) suppression   of the broadband amplified spontaneous emission (ASE) from the laser that   couples to other excited states.

%found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency. 
%The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser. 
%by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
%The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
%for a particular single photon detuning.

%in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning. (We can maybe add information about the prediction here?) 
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
%The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. 
When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B). The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) \mathrm{kHz}$. The molecule we form has a lifetime of $0.204(13) \mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified (or measured) directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

The ratio of molecule scattering rate to the Rabi frequency is larger than the theory prediction
by more than a factor of $10$.
Based on the calculation above, if this comes from the coupling to the $v'=0$ excited state,
it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
Additionally, coupling to other excited states can also add an offset to both the Raman
Rabi frequency and the scattering rate which can affect the scattering rate
to Rabi frequency ratio.

In order to verify whether any one of these known sources are the origin of the discrepancy,
we measured the Raman resonance as a function of the tweezer power and single photon frequency.
The important results from the fits are the 2 photon resonance frequency (light shift),
Raman Rabi frequency, atomic lifetime and molecular lifetime.
Each of these quantities provide us with information about a different combination
of physical processes and the detuning dependency of them allows us
to distinguish the contribution from the $v'=0$ excited states and other states.

First we look at the change in resonance frequency.
As a function of the tweezer power, we observe a linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ excited state,
we can further observe a $1/\delta$ component and a constant component
in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is predominantly due to the coupling between
the molecular state and the $v'=0$ excited state.
From this measurement, we can calculate a matrix element between the molecular state and
the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

@@

In order to calculate the matrix element ratio, we now need to extract the matrix element between the atomic state and the excited molecular state, $ \Omega_a $. We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
The atomic matrix element, $\Omega_a$,
is proportional to the the short range atomic wavefunction amplitude,
which scales as $P^{0.375}$ due to increasing density for weakly interacting particles.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$
within the range of confinement in our experiment.
Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
which agrees with our experimental result.
Similar to the light shift, there is also an offset and
a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi \times 5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi \times 11.53(16)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
which is in fact better than the theory prediction of $23.7$
and should not cause the scattering from the $v'=0$ state to be higher than expected.

Unfortunately, the offset in the Raman Rabi frequency fit cancels
the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
at the current detuning. However, this difference is not enough to explain
the difference we observed in the experiment.
The same offset will increase the Rabi frequency for blue detuning
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usable for the Raman transition.

>>>>

Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules. The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}. These requirements greatly limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

@@

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%,
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two coupling matrix elements here are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum. (See SM)

@@

% and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}
% As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states.
% Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$. \textcolor{blue}{(the two sentences have the same idea.)}
% it can be made larger by increasing the coupling of the atomic state with the excited molecular state.
Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs. Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $, where $ \omega_{\text{trap}} $ is the trap frequency. Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).

@@

For our system of Na and Cs atoms, we choose  a spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}. We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$. Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.

@@

% Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination.

@@

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
This spin flip selectively transfers atoms in the relative motion ground state \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer.
To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. %to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
% In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,
Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states.

% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser.
% by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
% for a particular single photon detuning.

% in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning. 
%(We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image. We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer. In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency. The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$. The molecule we form has a lifetime of $0.204(13) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

The ratio of the molecule scattering rate to the Rabi frequency is larger than the theory prediction by more than a factor of $10$. Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state, it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$. Additionally, coupling to other excited states can also add an offset to both the Raman Rabi frequency and the scattering rate which can affect the scattering rate to Rabi frequency ratio.

In order to verify whether any one of these known sources are the origin of the discrepancy, we measured the Raman resonance as a function of the tweezer power and single photon frequency. These dependencies allow us to experimentally determine the matrix elements, $ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift, or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.

% From these fits, we extract the 2 photon resonance frequency, Raman Rabi frequency, atomic lifetime and molecular lifetime.
%Each of these quantities provide us with information about a different combination of physical processes and the detuning dependency of them allows us to distinguish the contribution from the $v'=0$ excited states and other states.

First we look at the change in resonance frequency. As a function of the tweezer power, we observe the expected linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A). When we vary the tweezer frequency around the $v'=0$ intermediate state, we can further observe a $1/\Delta$ component and a constant background in the experimentally explored region. The background is caused by coupling to other excited states that are further away in energy. The $1/\Delta$ component, however, is due to the coupling between the molecular state and the $v'=0$ intermediate state. From this measurement, we can calculate a  $\Omega_m$ of $2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or $2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

@@

In order to calculate the matrix element ratio, we now need to extract the matrix element, $ \Omega_a $. We do this by measuring the dependencies of the Raman Rabi frequency, which depends on both $\Omega_m$ and $\Omega_a$. The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by tighter confinement at higher power (Fig.~\ref{f-det}B). Thus, as discussed before, for weakly interacting particles, $\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$. However, due to the strong interaction between the two atoms, this approximation breaks down. Instead, coupled-channel calculation shows that the scaling is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$, which agrees with our experimental result.
Similar to the light shift, there is also a constant background component and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$. The $v'=0$ component of the Raman Rabi frequency is $2\pi\times161.8(22) ~\mathrm{Hz\cdot mW^{-1.29}}$, or $2\pi \times 5.324(73)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power. Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi \times 11.53(16)\mathrm{MHz}$. This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$, which is in fact better than the theory prediction of $23.7$ and should not cause the ratio of the Raman Rabi frequency to scattering rate from the $v'=0$ state to be higher than expected. Furthermore, based on measurements of the excited state using photoassociation (PA) spectroscopy, the natural linewidth of the $v'=0$ excited state is no larger than $20 \mathrm{MHz}$. This suggests that the excited state linewidth should not cause a stronger than expected scattering from $v'=0$ state either.
